Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
minor fix in comment of Intro.

Hspec is thus useful for \emph{code documentation} but we observed that parts
of a specification can be useful as user documentation. We pay attention
to Python's Doctest~\cite{doctest} for this purpose.
Doctest is not commonly described as a BDD tool, but we think
it can be used for BDD.
There is a Haskell version of Doctest\footnote{%
http://hackage.haskell.org/package/doctest}.  It is integrated with with Haddock~\cite{haddock},
the standard documentation mechanism for Haskell.
It extracts \emph{interactive examples} in Haddock comments and
verify them automatically.

>>>>

Hspec is thus useful for \emph{code documentation} but we observed that parts
of a specification can be useful as user documentation. We pay attention
to Python's Doctest~\cite{doctest} for this purpose.
Doctest is not commonly described as a BDD tool, but we think
it can be used for BDD.
There is a Haskell version of Doctest\footnote{%
http://hackage.haskell.org/package/doctest}, which is integrated with Haddock~\cite{haddock},
the standard documentation mechanism for Haskell.
It extracts \emph{interactive examples} in Haddock comments and
verify them automatically.
